---
title: "Accessing relational databases with R"
output: 
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    toc: no
---

\newcommand{\exercise}[1]{\fbox{\parbox{\textwidth}{\bf \underline{Exercise:}\newline #1}}}

```{r setup, include=FALSE}
## set global chunk options
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
                      fig.align = "center")
```

---
```{r}
library(tidyverse)
library(odbc)
```
# Connect to database

```{r}
con <- dbConnect(odbc(),
                 driver = "ODBC Driver 17 for SQL Server",
                 server = "wi-projectdb.technikum-wien.at",
                 uid = "IMH", 
                 pwd = "imh")
dbListTables(con, schema = "dbo")
```

# More Secure Version

```{r}
con <- dbConnect(odbc(),
                 driver = "ODBC Driver 17 for SQL Server",
                 server = "wi-projectdb.technikum-wien.at",
                 uid = Sys.getenv("UID_FHTW_PROJECTDB"), 
                 pwd = Sys.getenv("PWD_FHTW_PROJECTDB"))

#Sys.setenv(UID_FHTW_PROJECTDB = "IMH", PWD_FHTW_PROJECTDB = "imh") # Set it in my Envirnment - NOT HERE
# Path for the File: C:\Users\exploFH\Documents\.Renviron <- Same as Above but strings are set without "

```

# Get Library Path

```{r}
.libPaths()
```


# Test SQL

```{r}
data = dbGetQuery(con, "select * from iris")
head(data)
```

# Integration with tidyverse

```{r}
irisdb <- tbl(con, "iris")
```

Query:

```{r}
results <- 
  irisdb %>%
  filter(Sepal_Width > 3) %>%
  group_by(Species) %>%
  summarise(Sepal_avg = mean(Sepal_Width), count = n()) %>%
  arrange(desc(count))
results
```

Behind the scenes:

```{r message=TRUE}
results %>% show_query()
```

# Integration with Markdown

```{r}
minlength = 3;
```

SQL Chunk (with `minsize` as parameter and `result` as output variable):

```{sql connection=con, output.var = "result"}
select Petal_Width from iris
where Sepal_Length > ?minlength
```

```{r}
head(result)
```


# Close connection

```{r}
dbDisconnect(con)
```

# Exercise

\exercise{Using the `iris` table, for each species, find out the number of flowers with a sepal length exceeding 3. Create both an SQL statement and an R statement using the tidyverse framework!}
