---
title: "Homework_3_wi19b004"
author: "Michael Scheidl"
date: "26 09 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment

Choose a web site of your choice that contains tabular data worth being harvested. You could look at sites like Wikipedia, or official sites like Statistik Austria offering information.
Retrieve the data using tidiyverse and rvest packages so it becomes a "tidy" tibble. If the data is in "wide" format, transform into long format. If it is in long format, transform into wide format. Document your steps in a Notebook.

# Solution

## Load Libraries

```{r message = FALSE, results='hide'}
library(tidyverse)
library(magrittr)
library(rvest)
```

## Load Website Source Code

```{r warning=FALSE, error=FALSE, results='hide'}
page <- read_html("https://de.wikipedia.org/wiki/Liste_von_Erdbeben_in_%C3%96sterreich")
html_nodes(page, "*") # Inspect Page Source

```

## Parse Table from HTML Code

```{r}
tmp <- 
  page %>%
  html_nodes("table") %>% # Search for table HTML-Nodes
  first() %>% # Use the First Node
  html_table() # Scrape table into tibble
tmp
```

## Clean Table


```{r}
tmp <- select(tmp,-last_col())
tmp <- tmp %>% mutate(across(where(is.character), ~na_if(., "-"))) %>% drop_na() # Convert - to NA and Filter wrong entries.
tmp <- tmp %>% mutate_all(str_replace_all, " Uhr", ":00") # Unify Time
tmp <- tmp %>% separate(`Zeit(UTC)`, c("Hour", "Minute"), sep = ":") %>% 
  mutate(Hour = str_pad(Hour, "0", width = 2, side = "left")) %>% 
  unite(Hour,Minute, sep = ":", col = "Zeit(UTC)") %>% 
  separate(`ZeitMEZ /MESZ`, c("Hour", "Minute"), sep = ":") %>% 
  mutate(Hour = str_pad(Hour, "0", width = 2, side = "left")) %>% 
  unite(Hour,Minute, sep = ":", col = "ZeitMEZ /MESZ") #Unify Time Columns
# Unify Month names -> Unifying the Complete Date didnt work´because of an issue with a " "-Error
tmp <- tmp %>% mutate_all(str_replace_all, "März", "Mrz.") 
tmp <- tmp %>% rename(Intentency = I, Magnitude = M, Depth = T) # Give the columns a speaking Name
tmp
```

## In Long Format


```{r}
tmp_long <- tmp %>%
  # Combine Intentency,Magnitude,Depth to column "Stat" and show the corresponding value in column "Value"
gather(key = "Stat", value = "Value", Intentency,Magnitude,Depth)
# Print Tibble sorted and redundant/unimportant columns hidden
tmp_long %>% arrange(`Datum(UTC)`) %>% select(-`ZeitMEZ /MESZ`,-Beschreibung) 
```


