---
title: "Sourcing html data with R"
output:
  pdf_document: 
    fig_caption: yes
    number_sections: yes
    toc: yes
  html_notebook: default
urlcolor: blue
---

# Task description

Parse course information from FH Technikum's CIS web site.

Steps:

- Explore html code
- Start parsing information for one course
- Create loop for getting several course infos

# Required packages

```{r message = FALSE}
library(tidyverse)
library(magrittr)
library(rvest)
```

# One course page

Example: Accounting in BWI1bb

URL: [https://cis.technikum-wien.at/addons/lvinfo/cis/view.php?lehrveranstaltung_id=34425&studiensemester_kurzbz=WS2018](https://cis.technikum-wien.at/addons/lvinfo/cis/view.php?lehrveranstaltung_id=34425&studiensemester_kurzbz=WS2018)

Load one page:

```{r }
page <- read_html("https://cis.technikum-wien.at/addons/lvinfo/cis/view.php?lehrveranstaltung_id=34425&studiensemester_kurzbz=WS2018")
```

Explore content:

```{r}
page
html_nodes(page, "*")
```

## Upper table

Idea:

- extract table using html_table()
- transpose table to get data column-wise

```{r}
tmp <- 
  page %>%
  html_nodes("table") %>%
  first() %>%
  html_table()
tmp
```

Transpose table:

```{r}
course <- tmp %>% select(X2) %>% t()
course
```

Fix column names:

```{r}
colnames(course) <- t(tmp[,1] %>% mutate_at("X1", str_replace, ":", ""))
course <- as.tibble(course, .name_repair = make.names)
```

Modify data types of numeric variables:

```{r}
course %<>%
  mutate(
    Semester = parse_integer(Semester),
    ECTS = parse_double(ECTS),
    Incomingpl채tze = parse_integer(Incomingpl채tze)
  )
course
```

## Lower table

Approach:

- Select section via `lvinfo` class
- Headings: all `<h2>` tags
- Content: all tags with `lv-info` class
- challenge: some sections have bullet points

```{r}
heads <- page %>%
  html_nodes(".lvinfo") %>%
  html_nodes("h2") %>%
  html_text()
heads
```

```{r}
FUN <- function(i) {
  if (length(html_children(i)))
      paste0(html_text(html_children(html_children(i))), collapse = "\n")
  else
     html_text(i)
}

values <- page %>%
  html_nodes(".lvinfo_data") %>%
  map(FUN)

values
```

create tibble and add to `course`:

```{r}
names(values) <- heads
course <- cbind(course, as.tibble(values))
```

## Combine to function

```{r}
parse_one_course <- 
  function(id = 34425, term = "WS2018")
  {
    ## get html
    url <- paste0("https://cis.technikum-wien.at/addons/lvinfo/cis/view.php?lehrveranstaltung_id=", id, "&studiensemester_kurzbz=", term)
    page <- read_html(url)
    
    ## upper table
    tmp <- 
      page %>%
      html_nodes("table") %>%
      first() %>%
      html_table()
    
    course <- tmp %>% select(X2) %>% t()

    #Diese Zeilen:
    #colnames(course) <- str_replace(tmp[,1], ":", "")
    #course <- as.tibble(course)

    #Durch diese ersetzt:
    colnames(course) <- t(tmp[,1] %>% mutate_at("X1", str_replace, ":", ""))
    course <- as.tibble(course, .name_repair = make.names)
    
    
    course %<>%
      mutate(
        Semester = parse_integer(Semester),
        ECTS = parse_double(ECTS),
        Incomingpl채tze = parse_integer(Incomingpl채tze)
      )
  
    ## lower table
    heads <- page %>%
      html_nodes(".lvinfo") %>%
      html_nodes("h2") %>%
      html_text()
    
    FUN <- function(i) {
      if (length(html_children(i)))
        paste0(html_text(html_children(html_children(i))),
               collapse = "\n")
      else
        html_text(i)
    }
    
    values <- page %>%
      html_nodes(".lvinfo_data") %>%
      map(FUN)
    
    names(values) <- heads
    course <- cbind(course, as.tibble(values))
    
    course
  }
```

# Loop over several courses

```{r}
parse_courses <- 
function(ids = 1, term = "WS2018")
{
    lapply(ids, parse_one_course, term)
    
}

ids = c(34509, 34473, 34496)
result <- 
  ids %>% 
  parse_courses %>%
  bind_rows()
summary(result)
```

