---
title: "LV5"
subtitle: "Single Variable Visualisation"
author: "Michael Scheidl"
date: "06 10 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      out.width = "70%", # make graphs smaller 
                      fig.align = "center") # center graphs
```

# Libraries {-}
```{r message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
```


# Overview

- Single Variable Visualisation
- Pie Charts
- Bar Charts
- Stacked Bar Charts
- Density Plot
- Boxplot
- Vilin Plot
- Mosaic Plot


# Plots fr a single Variable - bar plot

Create Dataset
```{r}
mtcars %>% 
  mutate(
    am = ifelse(am == 1, "manual", "automatic"),
    vs = ifelse(vs == 1, "straight", "v-shaped")
  ) -> data
```
## Classic Bar Chart


```{r}
data %>% ggplot(aes(x = am, fill= am)) + geom_bar()
```

[**Interpretation**]{.ul}:
- shows the number (count) of cars with automatic and manual shifting
- data set contains more cars with automatic shifting  than with manual shifting of gears

## Stacked Bar Chart

```{r}
data %>% ggplot(aes(x = "", fill = am)) +
  geom_bar(position = "fill", width = 0.5) +
  xlab("") +
  ylab("Proportion") +
  scale_x_discrete(breaks = NULL)
```
[**Interpretation**]{.ul}:

- the graph shows the proportion of automatic to manual gear shifting in the car data set

## Pie Chart

```{r}
ggplot(data, aes(x = 1, fill=am)) +
  geom_bar(position = "fill") +
  coord_polar("y") +
  xlab("") +
  ylab("Proportion") +
  ggtitle("Proportion of automatic and manual transmission") +
  scale_x_continuous(breaks = NULL) +
  #annotate("text", 0.3, 0.3, label="58,1%") +
  geom_segment(aes(x = 0.8, y = 0.8, xend = 0.9, yend = 0.9),
               arrow = arrow(length = unit(0.2, "cm")),
               col = "red") +
  annotate("text", 0.8, 0.8, label="58,1%")
```

[**Interpretation**]{.ul}:

- Different form of previous plot
- shows that 58.1% of the cars in the dataset are automatic transmission

## Graphs with two categorial variables

```{r}
data %>% ggplot(aes(x = am, fill=vs)) +
  geom_bar() +
  ggtitle("automatic/manual and straight/vshaped engine", subtitle="Number of cars")
```

[**Interpretation**]{.ul}:

- Number of cars with automatic gear shifting is higher than cars with manual gear shifting
- For automatic cars the v-shaped engines dominate (around 2/3)
- Manual transmission has approximately equal straight and vshaped engines

### Alternativ Switch variables

```{r}
data %>% ggplot(aes(x = vs, fill=am)) +
  geom_bar() +
  ggtitle("automatic/manual and straight/vshaped engine", subtitle="Number of cars")
```

[**Interpretation**]{.ul}:

- Doesnt change much for interpretation

## Stacked pie Charts - two categorial variables

```{r}
data %>% ggplot(aes(x = am, fill=vs)) +
  geom_bar(position = "fill") +
  ggtitle("automatic/manual and straight/vshaped engine", subtitle="Proportion of cars") +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = 8)
```


[**Interpretation**]{.ul}:

- Share of straight engines is lower with automatic gearbox than with manual gear boxes
- That more cars are automatic is no longer visible in the graph

### Alternative - switch variables

```{r}
data %>% ggplot(aes(x = vs, fill=am)) +
  geom_bar(position = "fill") +
  ggtitle("automatic/manual and straight/vshaped engine", subtitle="Proportion of cars") +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = 8)
```

## Grouped bar charts

```{r}
data %>% ggplot(aes(x = am , fill= vs)) +
  geom_bar(position = "dodge")
```

[**Interpretation**]{.ul}:

- Two groups are compares (automatic vs manual)
- In the group automatic the number of straight engines is lower the the number of v-shaped engines. In the group if manual shifting gear cars the opposite is the case.
- The number of straight engines appears to be equal in the group of automatic and manual cars

###Check number of cars via data manipulation

```{r}
data %>% group_by(am, vs) %>%  summarise(n=n())
```

[**Interpretation**]{.ul}:

- Indeed the number of cars with straight engines is equal in the group of automatic and manual cars.

# Exercise
Visualize the proportion of manufacturers among the shelves

```{r}
data(UScereal, package = "MASS")
head(UScereal)
```

```{r}
UScereal %>% mutate(shelf = as.factor(shelf)) %>% ggplot(aes(x = shelf, fill=mfr)) + geom_bar(position = "fill") + coord_flip()
#UScereal %>% mutate(shelf = as.factor(shelf)) %>% ggplot(aes(x = mfr, fill=shelf)) + geom_bar(position = "fill") + coord_flip()
```

# Once continous variable


## Histogram

```{r}
data %>% ggplot(aes(x = mpg, y = stat(density))) + geom_histogram(aes(fill = stat(density)), binwidth = 5) +
  scale_fill_distiller(type = "seq", direction = 1) +
  geom_density(col = "brown", size = 1)
```
## Boxplot

```{r}
ggplot(data, aes(1,mpg)) +
  geom_boxplot() +
  coord_flip() +
  xlab("")
```


```{r}
lm(hp ~ qsec, data = data)
```

```{r}
ggplot(data, aes(x = qsec, y = hp)) +
  geom_smooth(method = "lm") +
  geom_point() +
  annotate("label", 20, 200, label="hp=631.7 -27.17 qsec")
```
## Erklärende Variable sollten eig PS sein 

```{r}
ggplot(data, aes(x = hp, y = qsec)) +
  geom_smooth(method = "lm") +
  geom_point() +
  annotate("label", 200, 20, label="qsec=20,55 635 - 0.01846 hp")
```


## Scatter plot using labels

```{r}
data %>% rownames_to_column(var="name") %>% 
ggplot(aes(hp, qsec)) +
  geom_smooth(method = "lm") +
  geom_text(aes(label = name))
```

# Using `ggrepel` package

```{r}
library(ggrepel)
data %>% rownames_to_column(var="name") %>% ggplot(aes(hp, qsec)) +
  geom_point() +
  geom_text_repel(aes(label = name)) +
  geom_smooth(method = "lm") 
```
# One categorial and one numeric variable


## Boxplot
```{r}
ggplot(data, aes(factor(cyl), hp)) +
  geom_boxplot() +
  xlab("Cylinder")
```



## Violin plot

```{r}
ggplot(data, aes(factor(cyl), hp)) +
  xlab("Cylinder") +
  geom_violin()
```

[**Interpretation**]{.ul}:

- hp increases with number of cylinders
- very high horse power cars have all 8 cylinders

## Facetted Plot

```{r}
ggplot(data, aes(x = hp)) +
  geom_density() +
  facet_wrap(~cyl)
```

## Exercise 2

Visualize calories, given manufacturer

```{r}
head(UScereal, 1)

UScereal %>% ggplot(aes(x = calories, fill=mfr)) + geom_boxplot()

```










 
 