---
title: "WarmingUp"
subtitle: "BWI Specialisiation Data science"
author: "MS"
date: "8 9 2021"
output: 
  pdf_document:
      toc: yes
      toc_depth: 2
      number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE
                      #,results = 'hold' # For all Chunks
                      )
```

# Overview

-   IDE

-   Basic data structure in R

-   Advanced Data Structures in R

    -   `data.frame()`

-   Loops etc.

# IDE

Insert Chunks

-   Strg + Alt + I

Execute Chunk

 - Strg + Enter (Line of code in chunk)
 - Strg + Shift + Enter (Execute whole chunk)

Menu Help

-   Cheatsheets (Help -\> Cheat Sheets -\> RStudio IDE Cheat Sheet)

Comment Out/In code or text

- Strg + Shift + C

Keyboard Shortcut Help
 
 - Alt + Shift + K
 
Insert History (Tab History) into Code Chunk

  - Insert to Source
  
```{r}
vec_a = c(1,2,3)
vec_a
```

Many Tabs (lower right)

 - File
 - Packages
 - Help
 
 
```{r}
#?mean
#?str #Commented because its really going on my nerves!
```
 
Environment tab

 - Shows all defined variables in the code
 - available packages

 
# Basic data structures

Some Different basic data types in R are
 
 - integers
 - doubles
 - strings
 
data is organized in Vectors
```{r results='hold'}
vector_zahlen = c(1,2,5,7) #NOTE Chunk Option result='hold'
vector_zahlen
is.double(vector_zahlen)
is.integer(vector_zahlen)
```

Get integer Values:

```{r results='hold'}
vector_zahlen = c(1L,2L,5L,7L) #NOTE Force Integer Values
vector_zahlen
is.double(vector_zahlen)
is.integer(vector_zahlen)
```

Coersion of Basic data types

 - Vector of basic types can only have one type -> coersion

```{r results='hold'}
vector_mixed <- c(1.0, 1L, "Data Science", TRUE)
vector_mixed
```
- all coersed to character

Creating vectors shortcuts to c() combine function

```{r results='hold'}
c(1,2,3,4,5)
1:5
```

```{r results='hold'}
seq(1,10,2) # NOTE step size = 2
seq(from = 1,to = 10, by = 2)
seq.int(1,10,2)
```

```{r results='hold'}
is.integer(seq(1,10,2))
is.integer(seq(from = 1,to = 10, by = 2))
vector_integer <- as.integer(seq.int(1,10,2))
is.integer(as.integer(seq.int(1,10,2)))
```

Replicate Elements of a vector or list

```{r results='hold'}
# ?rep
rep(vector_integer, 3)
rep(vector_integer, each=3)
```


## Indexing Data

```{r results='hold'}
vector_zahlen[1:2]
vector_zahlen[c(1,2,4)]
```
## Named Vectors

```{r results='hold'}
vector_names <- c(zahl1 = 12L, zahl2 = 1212)
vector_names
```

Indexing Named Vector

```{r results='hold'}
vector_names[1] # NOTE Call Vector by Position
vector_names['zahl1'] # NOTE If Vector Elements have name you can call elements with name
```

Operations on vectors are vectorized

```{r results='hold'}
vector_integer * 1000 # NOTE Operation on all elements
```


```{r results='hold'}
vector_names <- c("Ben", "David", "Joe")
vector_names
paste(vector_names, "is a friend of mine")
```

Works on INT and Char vectors

# List

__A List is a generic vector:__
  - a list can contain different types (no coersion)
  
```{r results='hold'}
l <- list(1:3, "foo", 3.0, list(2, "bar"))
l
```

 - `[[]]` indication for a list



## Indexing a list

 - is a generic vector
  - can be indexed like a vector

```{r results='hold'}
l[1:2]
l[c(1,2)]
```


Get the content of a list entry

```{r results='hold'}
l[1] # NOTE a list
l[[1]] # NOTE a vector
is.list(l[1])
is.list(l[[1]])
```

- function `mean()` requires a numeric vector

```{r results='hold'}
mean(l[[1]]) # NOTE Works
try(
mean(l[1]) # NOTE Leads to error
)
```

## Named List

```{r results='hold'}
l_named <- list(a = 1:10, b = letters[1:10])
```
 

Indexing Named List:

```{r results='hold'}
# Extract element a with the numbers 1:10
l_named[[1]]
l_named$a # NOTE $ means a list -> doesn't work for a vector
l_named[["a"]]
```

```{r results='hold'}
#Returns a list
l_named["a"]
l_named[1]
```

# Attributes

 - Attributes add additional informations to an R object
 
```{r results='hold'}
vector_with_attribute <- 1:5
attr(vector_with_attribute, "creator") = "MyNameIsSlimShady"
attr(vector_with_attribute, "date") = "08.09.2021"
vector_with_attribute
```
 Show all Attributes of an Object with:
```{r results='hold'}
attributes(vector_with_attribute)
attributes(vector_with_attribute)$creator
```
 
## Zwei Spezielle Attribute

 - dim
 - class

```{r results='hold'}
x = 1:8
x
```


Set dim attribute

```{r results='hold'}
dim(x) <- c(2,4)
x
```

Create 3 Dimensional Array

```{r results='hold'}
dim(x) <- c(2,2,2)
x
```


Set Class Attribute

```{r results='hold'}
class(x) = "myclass"
attributes(x)

```


 - Dim and class are special attributes because R works differently when these are set, they are frequently employed attributes
 
# generic functions

 - Work with the class attribute
 - Use "myclass" from above
 
```{r results='hold'}
print.myclass <- function(x){
  cat("array dimension", dim(x), "\n")
}
```
 
Print an Object of class type "myclass"

```{r results='hold'}
x
```



# Data Frame

 - a list of named vectors
 - all vectors have the same length
 - an attribute for rows is set `row.names`
 
```{r results='hold'}
df <- data.frame(Name = c("Andi", "Sepp", "Horst"), Alter = c(23L,25L,38L))
df
```

Inspect df element
```{r results='hold'}
attributes(df)
```
Unclass df
```{r results='hold'}
df
unclass(df)
```


# Loops and [ls}apply

Instead of iterationg through a loop use `lapply` to apply a function to each element of the list.

```{r results='hold'}
lapply(df, summary)
```


```{r results='hold'}
lapply(df, length)
```


Simplify output (instead of a list a vector)

```{r results='hold'}
sapply(df, length)
```
























