---
title: "R Notebook"
author: "MS"
date: "8 9 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Lobraries {-}
```{r message=FALSE, warning=FALSE}
library(tidyverse)
```


# Overview

- `tibbles()`
- `select()`, `filter()`, `arrange()`, `mutate()`, `summarize()`, `group_by()`
- combine data from different tables
- Pipe `%>%`
- library("tidyverse")

# Tibbles

Tibbles are similar to `df`, but have slightly better printing behaviour.

```{r}
#iris
class(iris)
```


## Create `tibble()` from `data.frame`

```{r}
# ?as_tibble # NOTE Get Help of as_tibble from tidyverse package
# ?select # NOTE Get help from select() function
as_tibble(iris)
as_tibble(iris) %>% str()
```


- converts a `data.frame` to a `tibble`
- still is also a class `data.frame`

## Make `tibble`from `vector`

```{r}
tibble(Name = c("Tom", "Sepp", "Max"), Student = c(TRUE, FALSE, TRUE))
```


## Make `tibble`from `rows`

```{r}
# ?tribble ' Get help .... 
tribble( ~ Name, ~ Student, "Tom", TRUE, "Stefan", FALSE) 
```


# Select data variables

- Insert Pipe Shortcut -> Strg + Shift + M
- Knitten -> Strg + Shift + K

## Select with and without Pipe

```{r}
iris %>%as_tibble() %>% select(Species, Sepal.Length, Petal.Length) # NOTE Change Variable Order
select(as_tibble(iris), Species, Sepal.Length, Petal.Length)
```

## Select with helpers

```{r}
# ?select
```

Copied from help page

These helpers select variables by matching patterns in their names:

- starts_with(): Starts with a prefix.

- ends_with(): Ends with a suffix.

- contains(): Contains a literal string.

- matches(): Matches a regular expression.

- num_range(): Matches a numerical range like x01, x02, x03.


 select(starts_with)
```{r}
iris %>% as_tibble() %>% select(starts_with("s")) # NOTE Only Columns that starts with S or s

iris %>% as_tibble() %>% select(starts_with("s")) %>% select(ends_with("th"))
```


## Select with regex

- use `match()`for selection with regular expression

```{r}
iris %>% as_tibble() %>% select(matches("\\.")) # NOTE \\ is escape Sequence ofr \ 
```

Alternative:

```{r message=FALSE, error=FALSE}
iris %>% as_tibble() %>% select(matches(".*\\.")) 
```


Other variation of regular expression

```{r}
iris %>% as_tibble() %>% select(matches("[i]")) # NOTE alles mit i
```


## Filter Data rows

Help via RStudio
```{r}
#?filter
```

Help via Website
https://www.tidyverse.org/ bzw. https://dplyr.tidyverse.org/reference/filter.html


Stadard filter with multiple conditions

```{r}
iris %>%  as_tibble() %>% filter(Sepal.Length > 5) %>% filter(Sepal.Width == 3.9)
```

Alternatives:

```{r message=FALSE, error=FALSE}
iris %>%  as_tibble() %>% filter(Sepal.Length > 5 & Sepal.Width == 3.9)
iris %>%  as_tibble() %>% filter(Sepal.Length > 5, Sepal.Width == 3.9)

```

Standard filter with multiple **alternative** conditions

```{r}
iris %>%  as_tibble() %>% filter(Sepal.Length > 5 | Sepal.Width < 1) # Note || makes weird shit

```

Function alternatives

- `filter_if()`
- `filter_at()`


- fun TAB -> Function snippet for new function

```{r}

iris %>%  as_tibble() %>% filter_if(is.numeric, all_vars(. > 2)) #NOTE Check if column is Numeriv and check if <2
```
Alternative filter_if:
```{r message=FALSE, error=FALSE}
alalalla <- function(x) { #Funtion that alwas returns TRUE
  alalalla <- TRUE
}
iris %>%  as_tibble() %>% select(-Species) %>% filter_if(alalalla, all_vars(. > 2)) #Filter char column (Species) that <2 works
```


Filter_at



```{r}
iris %>% as_tibble() %>% filter_at(vars(ends_with("Length")), all_vars(. > 6.5)) # Erkl채rung: ??!?!?!??!? geht halt ..... alles f체rn arsch in der LV -.-
```


# Manipulate Data with `mutate()`

```{r}
iris %>% as_tibble() %>% mutate(Species = toupper(Species), Sepal.Length = 100 * Sepal.Length) %>% #NOTE Spalte 채ndern
  mutate(Sepal.Area = Sepal.Length*Sepal.Width, .before = Sepal.Length) # NOTE Spalte dazu an bestimmter stelle
```
## Set a column to `NULL`

```{r}
iris %>%  as_tibble() %>% mutate(Species = NULL)
```

Alternative:

```{r}
iris %>%  as_tibble() %>% select(-Species)
```

## Rename and add columns

```{r}
iris %>%  as_tibble() %>% rename("sepal_with" = Sepal.Width) # NOTE new_name = OLD_names
#rename_all(str_replace, "\\.", "_")
#rename_all(tolower)
```
# Sorting and summarize

```{r}

iris %>%  as_tibble() %>% select(ends_with("Length")) %>% arrange(Sepal.Length, desc(Petal.Length))
```

This is not the same as the following:
```{r}
iris %>% as_tibble() %>% select(ends_with("Length")) %>% arrange(Sepal.Length, desc(Sepal.Length)) %>% arrange(desc(Petal.Length))
```
## Summarize

```{r}
iris %>%  as_tibble() %>% summarise(mean_sepal_length = mean(Sepal.Length), mean_sepal_width = mean(Sepal.Width), max_sepal_length = max(Sepal.Length))
```

## Grouping

```{r}
iris %>%  as_tibble() %>% group_by(Species) %>% summarize(mean_sepal_length = mean(Sepal.Length), mean_sepal_width = mean(Sepal.Width), max_sepal_length = max(Sepal.Length))
```


# Combining tables

## Binding Tables

```{r}
A <- tibble(ID = c(1,2,5), Namen = c("Mike", "Stephn", "Joe"), Rating = c("AAA", "AA", "A"))
B <- tibble(ID = c(11,12,15), Namen = c("Monika", "John", "Harry"), Rating = c("AA", "AA", "A"))
bind_rows(A,B) # Kombiniert beide Tabellen reihenweise

C <- factor(c("M","M","M", "W", "M", "M")) #Zus채tzliche Spalte
bind_cols(bind_rows(A,B),gender = C) # Kombiniert
```

## Joining Tables

```{r}
combined_tables <- bind_cols(bind_rows(A,B),gender = C)
salary <- tibble(ID = c(1,2,11,15), wage = c(100,200,500,800))
```

### SQL like joins

```{r}
combined_tables %>% left_join(salary)
combined_tables %>% right_join(salary)
combined_tables %>% full_join(salary)
combined_tables %>% inner_join(salary)
```
 
 