---
title: "Exercise 3 (Web Scraping)"
author: "Georg Pretzner (wi19b013)"
date: "26 9 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---



# Task

Choose a web site of your choice that contains tabular data worth being harvested. You could look at sites like Wikipedia, or official sites like Statistik Austria offering information.
Retrieve the data using tidiyverse and rvest packages so it becomes a "tidy" tibble. If the data is in "wide" format, transform into long format. If it is in long format, transform into wide format. Document your steps in a Notebook.


# Datamanagement


## Required packages

```{r message = FALSE}
library(tidyverse)
library(magrittr)
library(rvest)
```


## WebScraping

The "Details table" from the website `https://en.wikipedia.org/wiki/List_of_Wikipedias` is scraped and then converted into the correct format.

The page source is written to the variable `wiki`.

```{r }
wiki <- read_html("https://en.wikipedia.org/wiki/List_of_Wikipedias")
```



Brief overview of the page source:

```{r}
wiki
html_nodes(wiki, "*")
```

# Tiding

The source of the website is filtered to tables and the third table is selected. Furthermore, 

```{r}
tmp <- 
  wiki %>%
  html_nodes("table") %>%
  nth(3) %>%
  html_table()
tmp
```


The columns `Language`, `Articles` and `Users` are extracted from the Details Table.

```{r}
NrArticlesCountry <- tmp %>% select(1,4,8)  %>% mutate_all(str_replace_all, ",", "")
NrArticlesCountry
```
# Transformation


Convert char fields with numeric value to integer:

```{r}
NrArticlesCountry %<>%
  mutate(
    Articles = parse_integer(Articles),
    Users = parse_integer(Users)
  )
NrArticlesCountry
```



## Convert to long format

The columns Articles and Users are grouped into one column and supplemented with the column Count.

```{r}
NrArticlesCountry_long <- NrArticlesCountry %>%
gather(key = "Type", value = "Count",
Articles, Users)
head(NrArticlesCountry_long)
```


## Convert to to wide format

The tibble changes again from the long format to the wide format.

```{r}
NrArticlesCountry_long %>% spread(Type,Count) %>% head()
```

