---
title: "Exercise 5 Pretzner"
subtitle: "Two Variable Visualisation"
author: "Georg Pretzner"
date: "10 10 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      out.width = "70%", # make graphs smaller 
                      fig.align = "center") # center graphs
```

# Libraries {-}
```{r message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(mosaicData)
```


# Exercise 5

For the following exercises, two variables are given. Choose a suitable visualization method for
each of them, and also for their relationship (so create three figures in total). Choose a “Brewer”
color palette (using scale_color_brewer(), scale_fill_brewer(), scale_color_distiller() or
scale_fill_distiller()).

Variables:

`wt` and `smoke` for the Gestation data (`mosaicData`)


# 

```{r}
data(Gestation, package = "mosaicData")
head(Gestation)
```



```{r}
ggplot(Gestation, aes(smoke, wt, fill=smoke)) + 
  geom_boxplot() + 
  xlab("Smoke") +
  scale_color_brewer(palette = 8)
```



```{r}
ggplot(Gestation, aes(x = wt, fill = wt)) +
geom_density() +
facet_wrap(~smoke)
```



