---
title: "Homework_2_wi19b004"
author: "Michael Scheidl"
date: "19 9 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment

The `Violations` data set in the `mdsr` package contains information regarding the outcome of health inspections of restaurants in New York City. Use these data to calculate the median violation score by zip code for zip codes in Manhattan with 50 or more inspections. What pattern do you see between the number of inspections and the median score.

# Solution

## Load Libraries

```{r error=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
```

This code block loads the library `tidyverse` for using `dplyr`, which contains tibbles and functions for transformations of dataframes. It also loads the `mdsr` package for the `Violations` data used in this exercise.

## Create Tibble

```{r }
data <- as_tibble(Violations)
```

Load the `Violations` data and save it in the variable `data` as tibble.

## Filter and Group desired Data


This codeblock filters the `Violations`data, to continue only with valid inspection data (inspection data after 1900.01.01) from Manhattan. After that the result is grouped by zipcode, camis (unique restaurant id), inspection date, inspection type and the score with summarise. This is done, to get only one entry per inspection, not per violation, because the violation score of the inspection is recorded with each violation. After that the inspections are grouped per zip code, the number of inspections and the meadian violation score per zip code is calculated. The result is filtered to only contain zip codes with 50 or more inspections. Information for the data set are from: https://data.cityofnewyork.us/api/views/43nn-pn8j/files/3016a624-55c0-4bd0-bfb4-95c6b9ea6ba4?download=true&filename=About_NYC_Restaurant_Inspection_Data_on_NYC_OpenData_092418.docx

```{r message=FALSE,results='hold'}
filtered_data <- data %>% 
  filter(boro == "MANHATTAN" & inspection_date > as.Date("1900-01-01")) %>% # Filter data for MANHATTAN and inspections_dates after 1900, because "Establishments with inspection date of 1/1/1900 are new establishments that have not yet received an inspection." 
  group_by(zipcode, camis,inspection_date, inspection_type, score) %>% # Group data to get unique inspections not violations
  summarise() %>% # Summarize data to get inspections
  group_by(zipcode) %>% # Only Group by zipcode
  summarise(number_of_inspections = n(), med_score = median(score, na.rm=TRUE)) %>% # Get number of inspections per ZIP Codes and the Meadian of the Inspectionscores
  filter(number_of_inspections >=50) # Only show zipcodes with more than 50 inspections
filtered_data
```


We can observe, that the median score is consistent at 12 after enough inspections are done, with only a few deviation zip codes. It is mostly lower when only 300 or less inspections are done.

```{r}
print(filtered_data %>% filter(number_of_inspections < 500), n = 12)
```

