---
title: "Importing tabular text data"
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    toc: yes
  word_document:
    toc: yes
---

\newcommand{\exercise}[1]{\vspace{0.5cm}\fbox{\parbox{\textwidth}{\bf \underline{Exercise:}\newline #1}}\vspace{0.5cm}}

---

```{r}
library(tidyverse)
```


# `read_delim()` and friends

## Data with delimiters

In general, `read_delim()` will do the trick (or one of the wrappers `read_csv()` for commas, `read_csv2()` for semi-colons, `read_tsv()` for tabulator, and `read_table()` for white space as separators):

```{r}
read_delim("data/text1.csv", delim = ",")
read_csv("data/text1.csv")
```

These functions try to guess the data types. If this does not work automagically, they can be specified:

```{r}
x = read_csv("data/text1.csv", col_types = "cdi-l")
x
```

Use `problems(x)` to diagnose issues:

```{r}
problems(x)
```

Alternatively, character columns can be transformed with `mutate()`:

```{r}
x = read_csv("data/text1.csv", col_types = "ccddc")
x
x %>% mutate(Sepal.Length = parse_double(Sepal.Length),
             Sepal.Width = parse_double(Sepal.Width))
```

## Fixed-width data

Text columns can be a mess if not properly quoted.

```{r}
read_delim("data/text2.txt", delim = " ")
```

 `read.fwf()` can help here:

```{r}
data <- read_fwf("data/text2.txt", 
                 fwf_cols(Name = 13, Address = 35, Tel = 15))
data
```

\exercise{Try to read in the data sets \texttt{dataXX.txt} provided in the file \texttt{data.zip}}

```{r}
read_delim("data/data1.txt") # Data is shit -> sep and decimal
read_delim("data/data2.txt", col_names = FALSE) # No Header
d3 <- read_fwf("data/data3.txt", col_positions = fwf_widths(c(15,15,8,10,6,10,9,12,19,18))) # Read with fixed col width
names(d3) <- d3[1,] # Add headers (from first data line)
d3 <- x[-1,] # (remove first data line -> header)
d3
d4 <- read_table("data/data4.txt")
d4

```



# Separating/joining columns

Separate:

```{r}
data2 <- data %>% 
  mutate(Address = str_replace(Address, ",", ";")) %>% 
  separate(Address, c("Street", "ZIPCity"), sep = "; ") %>% 
  separate(ZIPCity, c("ZIP", "City"), sep = " ")
data2
```

... and join again:

```{r}
data2 %>% 
  unite(ZIPCity, ZIP, City, sep = " ") %>% 
  unite(Address, ZIPCity, Street, sep = ", ")
```

\exercise{Using the data below, transform the birth date into the format \texttt{YYYY-MM-DD}. Try to pad days and months with a leading 0, so that, e.g., \texttt{1.1.1988} becomes \texttt{1988-01-01}. (Hint: use \texttt{mutate()} with \texttt{str\_pad()}).}

```{r}
tribble(~Name, ~Birthdate,
        "Susan", "29.10.1966",
        "Will", "1.1.1988",
        "Chris", "10.10.1977") %>% 
  separate(Birthdate, c("Tag", "Monat", "Jahr"), sep = "\\.") %>% #Seperate Tag Monat Jahr -> seperator .
  mutate(Tag = str_pad(Tag, "0", width = 2, side = "left")) %>% 
  mutate(Monat = str_pad(Monat, "0", width = 2, side = "left")) %>% 
  unite(Jahr, Monat, Tag, sep = "-", col = "Birthdate")

```

# Wide and long format

Sometimes, values of one variable are "pivoted" into columns:

```{r}
head(USArrests)
USArrests %>% as_tibble() # NO ROWNAMES
USArrests %>% rownames_to_column("State") %>% as_tibble() # Use State as Rownames
USArrests %>% as_tibble(rownames = "State") # Use State as Rownames
```

Use `gather()` to transform the data into "long" format:

```{r}
arrests_long <- USArrests %>% 
  rownames_to_column("State") %>%  ## to keep info -- gather() will remove rownames
  gather(key = "Crime", value = "Arrests",
         Murder, Assault, Rape)
head(arrests_long)
```

## `pivot_longer`

```{r}
data_long <- USArrests %>% rownames_to_column("State") %>% pivot_longer(cols = c("Murder", "Assault", "Rape", "UrbanPop"), names_to = "Type")

```
## `pivot_wider`

```{r}
data_long %>% pivot_wider(names_from = "Type")
```


... and `spread()` for transforming "long" into "wide" format:

```{r}
arrests_long %>% spread(Crime, Arrests) %>% head()
```

\exercise{The \texttt{sleep} data in R is about \texttt{extra} sleep time of 10 students caused by two drugs (\texttt{group}). Transform the data into wide format, so that the timings for the two drugs are represented in two separate columns. Compute, for each student, the difference in extra sleep time and add this to the data.}

# Missing data

```{r}
data = read_table("data/text3.txt", col_names = TRUE, na = "??")
```

```{r}
data <- data %>% 
  mutate_all(na_if, "") %>% 
  fill(Class, Sex, .direction = "down") 
```

Regular NA handling:

```{r}
data %>% filter(!complete.cases(.)) # find all rows with missings

data %>% drop_na() ## either drop them ...
data %>% mutate(Survived = replace_na(Survived, 0)) ## ... or replace them
```

\exercise{Using the data below, first find out all rows with missing data. Impute missing invitations with 0, and missing ages with the average age. Remove all rows with other missings.}

```{r}
tribble(~Name, ~Age, ~Invitations, ~Phone,
        "Tim", 20, 0, "123 345",
        "Mary", 30, 12, "321 999",
        "Chris", 25, NA, "444 324",
        "Lilly", NA, 0, "453 424",
        "Will", 20, 0, NA
)
```

