---
title: "Homework_4_wi19b004"
author: "Michael Scheidl"
date: "03 10 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center") # , out.width = "70%"
```

# Assignment

The MLB teams data set in the mdsr package contains information about Major League Baseball teams in the past four seasons. There are several quantitative and a few categorical variables present. See how many variables you can illustrate on a single plot in R . The current record is 7. (Note: This is not good graphical practice— it is merely an exercise to help you understand how to use visual cues and aesthetics!)

# Solution


## Libraries
```{r message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(mdsr) 
```

## Inspect Data

```{r}
#?MLB_teams
head(MLB_teams, 1) %>% as_tibble()
```

## Plot

```{r}
g <- MLB_teams %>% as_tibble() %>%
# Put data in ggplot2 with Payroll on the x and attendace on the y axis
  ggplot(aes(x=payroll,y=attendance)) + 
# Use normalized Attendance as Size, HomeTowns population as Color
  geom_point(aes(size=normAttend, col = metroPop, 
# Leage as Shape and WinningPercentage as Alpha Value
                 shape=lgID, alpha=WPct)) + 
  facet_wrap(~yearID) + # Split Plot per Season
  geom_text(aes(label = teamID)) + # Add Team Name as Label
  xlab("Teamsalary") + # Label X Axis
  ylab("Attendend Fans") + # Label Y Axis
  labs(
# Set a Meaningfull Title and subtitle to describe Plot and used Dataset
     title = "Attendend Fans with respect to Teamsalary", 
     subtitle = paste(nlevels(as_factor(MLB_teams$teamID)), "Teams over", 
                      nlevels(as_factor(MLB_teams$yearID)), "Years")) 
# NOTE: Could not resize the plotting Area to show complete Legend and Texts
g # Show Plot
```

Illustrated 7 Variables in one (very small) Plot and tied the record.