---
title: "LV4"
subtitle: "ggplot2 Package"
author: "Michael Scheidl"
date: "29 09 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      out.width = "70%", # make graphs smaller 
                      fig.align = "center") # center graphs
```

# Libraries {-}
```{r message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
```

\newcommand{\exercise}[1]{\fbox{\parbox{\textwidth}{\bf \underline{Exercise:}\newline #1}}}

# Overview

- Plotting different data variables in graphs
- using `ggplot2` package


# Data

- `disp`means displacement in `in²`
- `wt` means weight in `1000 lbs`


```{r}
# ?mtcars
mtcars %>% knitr::kable(caption = "Data for Visualisation")
```

# Using `ggplot` Framework

```{r}
ggplot(mtcars)
```


## Add aestetics

```{r}
g <- mtcars %>% ggplot(aes(x=disp,y=mpg))
g
```

## Add Datapoints

```{r}
g + geom_point()
```

## Add Line

```{r}
g + geom_line() # Note - not very useful
```



## Add more variables

```{r}
g <- mtcars %>% rownames_to_column("car_name") %>% as_tibble() %>% ggplot(aes(x=disp,y=mpg)) + geom_point(aes(size=qsec, col = cyl)) +
xlab("engine size") +
ylab("Mile per Gallon") +
labs(caption = "Fuel efficiency", title = "Miles different cars achieve w.r.t. engine size", subtitle = paste("Number of cars", nrow(mtcars))) #+ # paste0 = paste without " "
  #geom_text(aes(label = car_name)) # Add text to points
g
```
### Interpretation

- Engine Size and miles per gallon have a relation 
  - the higher the engine size the lower a car can travel per gallon
  
- bigger engine size goes together with a larger number of cylinders
- very small engine size have highqsec

## facets

```{r}
g + facet_wrap(~gear)
```

# Exercise

  \exercise{Using the \texttt{UScereal} data from the \texttt{MASS} package, visualize the relationship of calories, sugars and fat. Additionally, highlight whether the product has been enriched with vitamins. Use appropriate titles and legends.}
\exercise{As an extension to the previous plot, show the information separately for each manufacturer, using facets. Similarly, create a plot for the shelves using groups.}

## Data `UScereal`

```{r}
data(UScereal, package = "MASS")
UScereal
```
```{r}
g2 <- UScereal %>% rownames_to_column("Name") %>% as_tibble() %>% ggplot(aes(x=sugars,y=calories)) + geom_point(aes(size=fat, col = vitamins)) +
  labs(caption = "US Cerial for diets", title = "kcal w.r.t. sugars", subtitle = paste("Number of searials in Dataset", nrow(UScereal)), y = "Sugarcontent", x = "Calories kcal")
g2

# scale_color_brewer(palette = "red")
# theme(legend.position = "left")
```
```{r}
g2 + facet_wrap(~mfr)
g2 + geom_smooth(aes(group = shelf))
```

