---
title: "R Warmup - Exercise Sheet - wi19b004"
author: "Michael Scheidl"
date: "13 9 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---


# Assignment

Create a function varyvec(a, b) that returns a list with the following integer vectors:
- sequence from a to 1
- sequence of all even integers from a to 1
- sequence of all odd integers from a to 1
- sequence of all squared integers from a to 1
- sequence of all integers from a to 1, not smaller than b

Each list component should be named appropriately. The list should be of class varyvec. Implement a print
method that for each vector, only prints the first and the last element (separated with ...) Demonstrate
the functions using a small example. Also show the “raw” return value (using unclass()). Document all
steps in an R-Markdown-notebook and upload the PDF on Moodle.

# Solution

## Override Print for varyvec Class

```{r results='hold'}
print.varyvec <- function(a){
  lapply(a, custprint)
}
```

This codeblock overrides the print functionality for Variables of the Class `varyvec`.
`lapply` calls the custom function `custprint` for each vector in the list a.


## Define Function for Custom Output

```{r results='hold'}
custprint <- function(a){
  cat(a[1],"...", a[length(a)-1], "\n", sep="")
}
```

This function is called by the custom `print()` function for the class `varyvec`. It prints the first element of the provided `a` vector with `a[1]` and the last element of the vector with `a[length(a)-1]`. It concatenates "..." in between and a new line at the end, with no separator between via the function `cat()`.


## Define varyvec Function as required

```{r results='hold'}
varyvec <- function(a,b){
  retlist <- list(seqfromAto1 = a:1, seqevenintfromAto1 = as.integer(subset(a:1L, a:1L %% 2L == 0L)), seqoddintfromAto1 = as.integer(subset(a:1L, a:1L %% 2L == 1L)), seqsquaredintfromAto1 = as.integer((a:1L)^2), seqsquaredintfromAto1smallerB = as.integer(subset(a:1L, a:1L > b)))
  class(retlist) <- "varyvec"
  varyvec <- retlist
}
```

Defines the Function `varyvec(a, b)` and creates a list of vectors. These are:

  - sequence from a to 1 with `a:1`
  - sequence of all even integers from a to 1 with `as.integer(subset(a:1L, a:1L %% 2L == 0L))`
    - The subset ensures, that the modulo of 2 is 0, which are only even numbers
  - sequence of all odd integers from a to 1 with `as.integer(subset(a:1L, a:1L %% 2L == 1L))`
    - The subset ensures, that the modulo of 2 is 1, which are only odd numbers
  - sequence of all squared integers from a to 1 with `as.integer((a:1L)^2)`
  - sequence of all integers from a to 1, not smaller than b with `as.integer(subset(a:1L, a:1L > b))`
    - The subset ensures, that no number is smaller than b
It also sets the class of the list to `varyvec` and returns it.


## Show RAW Output of varyvac

```{r results='hold'}
unclass(varyvec(10L,4L))
```

The `unclass()` ensures, that the custom print function isn´t called. This Output shows, that the returned list of `varyvec` contains all correct vectors in a named list.

## Show functionality
```{r results='hold'}
returnlist <- varyvec(10L,4L)
returnlist
```

This codeblock calls the `varyvec(a,b)` function and stores it´s return value in the variable `returnlist`. When printing this variable, the overridden print function is executed, which prints only the required output for each vector.