---
title: "HomeWork 1 - R Warmup wi19b013"
author: "Georg Pretzner"
date: "13 9 2021"
output: 
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
---


```{r}
plot(presidents)
```


# Exercise 18 (Pretzner)

Create a list that contains the data sets presidents, iris, Nile, and HairEyeColor. Create a function myclasses(x) taking a list of data sets and returning a named vector with the classes for each data set (use class()). The return value should be of class “myclasses”. Implement a print method that just informs about the total amount of data sets, and prints a comma-separated list of the data set names (use names()) and their corresponding data set class. Demonstrate the functions with the list initially created. Document all steps in an R-Markdown-notebook and upload the PDF on Moodle.





```{r}
myclasses <- funtion(x){
  myclasses <- 
  return(myclasses)
}

```


# Datenstreckbrief

List with Presidents, iris, Nile, and HairEyeColor

```{r}
l <- list(presidents, iris, Nile, HairEyeColor)

l
```





Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
